### 2021-03-12 paper_1.tex
1.4.4

\subsubsection{\emph{Salient Object Detection}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
    \centering
    \caption{Metrics comparison}
    \label{fig: metrics}
\end{figure}
To compare the performance of the salient object detection, metrics such 
as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
results showed that for the first two metrics (P-R), systems such as HS and 
RF are the best, while for the F-score the proposed method is able to consider 
a greater range of thresholds. As it can be seen, in these two metrics the 
proposed system (CGVS (t2)) considers the central bias unlike the others. 
If the central bias were not considered, the results decrease but are still 
satisfactory (CGVS ''). However, in the remaining two metrics, the proposed 
system is the best, except in the PASCALS dataset where the best is the RF 
method.

>>>>

\subsubsection{\emph{Salient Object Detection}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
    \centering
    \caption{Metrics comparison}
    \label{fig: metrics}
\end{figure}
To compare the performance of the salient object detection, metrics such 
as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
results showed that for the first two metrics (P-R), systems such as HS and 
RF are the best, while for the F-score the proposed method is able to consider 
a greater range of thresholds. As it can be seen, in these two metrics the 
proposed system (\emph{CGVS($ t_2 $)}) considers the central bias unlike the others. 
If the central bias were not considered, the results decrease but are still 
satisfactory (\emph{CGVS''}). However, in the remaining two metrics, the proposed 
system is the best, except in the PASCALS dataset where the best is the RF 
method.

\subsubsection{\emph{Between Saliency Map and Salient Object}}
Most fixation prediction methods perform poorly when used to detect salient 
objects. To solve this problem, a two-dimensional Gaussian distribution is 
applied to each salience map derived from any method. The derived output 
will be used as an initial CBSP from which the salient objects can be 
extracted with the previously proposed calculations. The metrics, used to 
measure the performance of the different methods, improve if the methods 
replace their salience map with CBSP.
